### 2023-02-15 README.Rmd
Update README and bump version ref #44
Fix issues from WinBuilder and r-hub [no CI]

**Important:** This package is in a very early stage. API might still change.

@@

```r
library(rang)
resolve(pkgs = c("sna", "schochastics/rtoot"), snapshot_date = "2022-11-30")
```

@@

```{r example2}
graph$deps_sysreqs
```

@@

[^gesis]: It stands for "R Archiving Nerds at GESIS". The package was previously named `gran`, but we decided to rename it to `rang` because there is another package named [gRAN](https://cran.r-project.org/web/packages/GRANBase/vignettes/GRAN_Overview.html).

>>>>

@@

```r
library(rang)
x <- resolve(pkgs = c("sna", "schochastics/rtoot"), snapshot_date = "2022-11-30")
```

@@

```{r example2}
graph$sysreqs
```

@@

[^gesis]: It stands for "R Archiving Nerds at GESIS". The package was previously named `gran`, but we decided to rename it to `rang` because there is another package named [gRAN](https://CRAN.R-project.org/package=GRANBase).
